---
title: 'Tidy Tuesday 06-04: Ramen'
output:
  html_document:
    df_print: paged
---

This is a rough first attempt at a Tidy Tuesday writeup! Starting with June 6th, 2019:

https://github.com/rfordatascience/tidytuesday/tree/master/data/2019/2019-06-04

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(tidytext)
ramen_ratings <- readr::read_csv("https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2019/2019-06-04/ramen_ratings.csv")
colnames(ramen_ratings)

```
First, I used head() and summary() to get a quick sense of what this data looks like:

```{r}
head(ramen_ratings)
```

```{r}
summary(ramen_ratings)
```

The first question that jumped out at me: how do the median ratings (and distribution of ratings) differ between countries? What is best and worst country for ramen? A horizontal box plot seems like a good way to get started:

```{r warning=FALSE}
ramen_ratings %>%
  ggplot(aes(x=fct_reorder(country, stars, fun=median), y=stars)) + 
    geom_boxplot() + 
    coord_flip()
```

Here I noticed some strange behaviors -- in particular, take a look at the highest-ranked countries. It appears that United States is both first-ranked and, somehow, has a lower median rating than Japan! How is that? After poking around, I realized that the "fun=median" parameter passed into ggplot2's did not identify outliers, whereas ggplot2's boxplot geom identifies outliers and generates the 25th-50th-75th percentile box excluding those outliers. How could we get "fun=median" to behave similarly?

For the time being, I proceeded to visualizing by style (and noticed the same median ranking issue yet again!)


```{r}
ramen_ratings %>%
  ggplot(aes(x = fct_reorder(style, stars, fun=median, .desc=TRUE), y=stars)) +
        geom_boxplot(aes(fill = fct_reorder(style, stars, fun=median, .desc=TRUE))) +
        # geom_jitter(position=position_jitter(0.2)) +
        theme_bw(base_size = 14) +
        xlab("Style") +
        ylab("Ratings") +
        scale_fill_discrete(guide = guide_legend(title = "Style"))
```
The lack of a box for Can made me realize, oh wait, is there only one observation with a Can style in our dataset? Can we do some simple low-pass filtering to get more focused data? Sure enough:

```{r}
ramen_ratings %>%
  group_by(style) %>%
  count()
```

For simplicity's sake, I decided to exclude Bar, Can, and Restaurant, as well as ramen with Null Style values. I wanted to compare these newly simplified distributions, and sure enough, take a look at the disparity between Box and Cup ramen!:

```{r}

ramen_cleaner <- ramen_ratings %>%
  filter(style != "NA" & style != "Bar" & style != "Can" & style != "Restaurant")
  

ramen_cleaner %>%
  ggplot(aes(x = stars, fill=style)) +
        geom_density(alpha=0.3)
```

Now let's redo box plots excluding low-count styles:


```{r}

ramen_cleaner %>%
  ggplot(aes(x = fct_reorder(style, stars, fun=median, .desc=TRUE), y=stars)) +
        geom_boxplot(aes(fill = fct_reorder(style, stars, fun=median, .desc=TRUE))) +
        # geom_jitter(position=position_jitter(0.2)) +
        theme_bw(base_size = 14) +
        xlab("Style") +
        ylab("Ratings") +
        scale_fill_discrete(guide = guide_legend(title = "Style"))
        
```
## Part Two: Text Analysis

After poking around other Tidy Tuesday projects, I noticed that there were some interesting things happening in that unstructured "brand" text variable:


```{r}
all_words_in_variety <- ramen_ratings %>%
  unnest_tokens(word, variety) %>%
  select(word)

words_sorted <- all_words_in_variety %>%
  group_by(word) %>%
  count() %>%
  arrange(desc(n))

words_sorted

```

A quick densit plot reveals that most brand words are relatively unique across all observations:

```{r}
words_sorted %>%
  ggplot(aes(x=n)) +
  geom_density()
```

I decided to extract meat type (I term this "variety"). To do this, I use the grepl() search, which checks to see if a substring exists within a string. Combined with case_when() and mutate(), I can generate the appropriate value for our new "variety" variable based on the result of these substring searches:

```{r}
ramen_ratings <- ramen_ratings %>%
  mutate(variety = tolower(variety)) %>%
  mutate(meat = case_when(
    grepl("chicken", variety) ~ "chicken",
    grepl("beef", variety) ~ "beef",
    grepl("pork", variety) ~ "pork",
    grepl("shrimp", variety) ~ "shrimp",
    grepl("seafood", variety) ~ "seafood"))

ramen_ratings %>%
  group_by(meat) %>%
  count()
```

```{r}
ramen_ratings %>%
  filter(!is.na(meat)) %>%
  ggplot(aes(x = fct_reorder(meat, stars, fun=median, .desc=TRUE), y=stars)) +
        geom_boxplot(aes(fill = fct_reorder(meat, stars, fun=median, .desc=TRUE))) +
        # geom_jitter(position=position_jitter(0.2)) +
        theme_bw(base_size = 14) +
        xlab("Meat") +
        ylab("Ratings") +
        scale_fill_discrete(guide = guide_legend(title = "Meat"))
```

I waas actually quite surprised by the similarity across meat types! Perhaps the biggest difference is that pork has the widest interquartile range -- which suggests that pork is the riskiest bet when picking up some random ramen! Sure enough: 

```{r}
ramen_ratings %>%
  filter(!is.na(meat)) %>%
  ggplot(aes(x = stars, fill=meat)) +
        geom_density(alpha=0.3)
```

I repeated the process for "spicy", which I generated as a boolean variable based on the same substring grepl() search method:

```{r}
ramen_ratings <- ramen_ratings %>%
  mutate(variety = tolower(variety)) %>%
  mutate(is_spicy = grepl("spicy", variety))
```

```{r warning=FALSE}
ramen_ratings %>%
  ggplot(aes(x = stars, fill=is_spicy)) +
        geom_density(alpha=0.3)
```

Really not much of a difference! As my last technique, I repeated this approach for curry:

```{r}
ramen_ratings <- ramen_ratings %>%
  mutate(variety = tolower(variety)) %>%
  mutate(is_curry = grepl("curry", variety))
```

```{r message=FALSE, warning=FALSE}
ramen_ratings %>%
  ggplot(aes(x = stars, fill=is_curry)) +
        geom_density(alpha=0.3) +
        theme_bw(base_size = 12) +
        xlab("Rating (out of 5)") +
        ylab("Density") +
        scale_fill_discrete(guide = guide_legend(title = "Curry?"))
```

Ah ha! I was very pleased to see that yes, it appears curry brands consistently rate higher than non-curry brands. Very happy to see this result. And here are the numbers per class, for reference:

```{r}
ramen_ratings %>%
  group_by(is_spicy) %>%
  count()
```

